---
title: "DAT301 Midterm Project"
author: "Amber Kahklen, Shaira Alam, Alyssa Stefencavage"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
df = read.csv("/Users/amber/Downloads/adultdata.csv") #you will have to change this to your directory when working on it
colnames(df) <-c("age", "workclass", "fnlwgt", "education", "education-num", "marital-Status", "occupation", "relationship", "race", "sex", "capital-gain", "capital-loss", "hours-per-week", "native-country", "wage_below_orAbove_50k")

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Embed html webpage

Taken from Johns Hopkins University website: [https://coronavirus.jhu.edu/map.html](https://coronavirus.jhu.edu/map.html)

<iframe src="https://coronavirus.jhu.edu/map.html"></iframe>
