---
title: "DAT301 Midterm Project"
author: "Amber Kahklen, Shaira Alam, Alyssa Stefencavage"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
df = read.csv("adultdata.csv") #you will have to change this to your directory when working on it
colnames(df) <-c("age", "workclass", "fnlwgt", "education", "education-num", "marital-Status", "occupation", "relationship", "race", "sex", "capital-gain", "capital-loss", "hours-per-week", "native-country", "wage_below_orAbove_50k")
library(ggplot2movies)
library(dplyr)
library(ggplot2)
adultData <- data.frame(df)
```
## Income Prediction | Based on Census Data

UCI's Machine Learning Repository, Adult Data Set: https://archive.ics.uci.edu/ml/datasets/Adult

- Predicts if income is above or below $50,000 based on census data


## Categories of Adult Income Data

<font size = "3">**age**: continuous.

**workclass**: Private, Self-emp-not-inc, Self-emp-inc, Federal-gov, Local-gov, State-gov,    Without-pay, Never-worked.
            
**fnlwgt**: continuous.

**education**: Bachelors, Some-college, 11th, HS-grad, Prof-school, Assoc-acdm, Assoc-voc, 9th, 
            7th-8th, 12th, Masters, 1st-4th, 10th, Doctorate, 5th-6th, Preschool.
            
**education-num**: continuous.

**marital-status**: Married-civ-spouse, Divorced, Never-married, Separated, Widowed, 
                Married-spouse-absent, Married-AF-spouse.
                
**occupation**: Tech-support, Craft-repair, Other-service, Sales, Exec-managerial, Prof-specialty, 
            Handlers-cleaners, Machine-op-inspct, Adm-clerical, Farming-fishing, Transport-moving,             Priv-house-serv, Protective-serv, Armed-Forces.
            
**relationship**: Wife, Own-child, Husband, Not-in-family, Other-relative, Unmarried.

**race**: White, Asian-Pac-Islander, Amer-Indian-Eskimo, Other, Black.

**sex**: Female, Male.</font>

## Categories of Adult Income Data Continued

<font size = "3">**capital-gain**: continuous

**capital-loss**: continuous

**hours-per-week**: continuous.

**native-country**: United-States, Cambodia, England, Puerto-Rico, Canada, Germany, 
                  Outlying-US(Guam-USVI-etc), India, Japan, Greece, South, China, Cuba, Iran,                       Honduras, Philippines, Italy, Poland, Jamaica, Vietnam, Mexico, Portugal,                         Ireland, France, Dominican-Republic, Laos, Ecuador, Taiwan, Haiti, Columbia,                      Hungary, Guatemala, Nicaragua, Scotland, Thailand, Yugoslavia, El-Salvador,                       Trinadad&Tobago, Peru, Hong, Holand-Netherlands.</font>

## 1. What is the capital gain based on age?  

```{r}
education  <- adultData %>% count(education)

Levels <-c("Bachelors", "Some-college", "11th", "HS-grad", "Prof-school", "Assoc-acdm", "Assoc-voc", "9th", 
            "7th-8th", "12th", "Masters", "1st-4th", "10th", "Doctorate", "5th-6th", "Preschool")
Count <- c(education$n)

genres_plot <- data.frame(education)
ggplot(genres_plot, aes(x=Levels, y=Count, fill=Levels)) + 
geom_bar(stat="identity")

```

## 2. Does the workclass affect if the individual make above or below 50k a year

```{r}

```

## 3. Hours per week vs above or below 50k a year (boxplot)

```{r}

```

## 4. Does making above or below 50k have an impact on marital status?

```{r}

```

## 4. Does gender have an effect on wages?

```{r}

```

## 6. Does the hours per week affect relationship and marital status?

```{r}

```

## 7. Does occupation and education affect wage?

```{r}
boxplot(df$hours-per-week~df$wage_below_orAbove_50k)
```


## Embed html webpage

Taken from Johns Hopkins University website: [https://coronavirus.jhu.edu/map.html](https://coronavirus.jhu.edu/map.html)

<iframe src="https://coronavirus.jhu.edu/map.html"></iframe>
